Interactive Filter and Display of Hillary Clinton's Emails: \\A Cautionary Tale of Metadata

### 2017-04-03 VAST_submission/vgtc_journal_latex/paper.tex
Added Bacon reference

It is quite possible that we will only see what we want to see in the data.  The human tendency to seek out information that confirms our preconceptions has been well known since Francis Bacon first wrote in the \emph{Novum Organum},1620
\begin{quotation}
``The human understanding, once it has adopted opinions, either because they were already accepted and believed, or because it likes them, draws everything else to support and agree with them.
\end{quotation}
This is now called confirmation bias \cite{confBias} and it plagues much modern discussion, particularly on the internet and social media.

>>>>

It is quite possible that we will only see what we want to see in the data.  The human tendency to seek out information that confirms our preconceptions has been well known since 1620 when Francis Bacon first wrote 
\begin{quotation}
``The human understanding, once it has adopted opinions, either because they were already accepted and believed, or because it likes them, draws everything else to support and agree with them.''

\noindent
Francis Bacon, \emph{Novum Organum}, Book 1, Aphorism 46 \cite{Bacon1620}

\end{quotation}
This is now called confirmation bias \cite{confBias} and it plagues much modern discussion, particularly on the internet and social media.
